---
title: "Introduction to binomial"
author: "Jennifer Shim"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```


## Binomial

The package `"binomial"` is an R package that implements functions for
calculating probabilities of a Binomial random variable, and related calculations such as the
probability distribution, the expected value, variance, etc.


## Function bin_choose()

This function calculates the number of combinations in which k successes can occur in n trials.

```{r}
bin_choose(5, 2)
bin_choose(5, 0)
bin_choose(5, 1:3)
```

## Function bin_probability()

This function checks for valid trials, prob, and success and get probabilities of getting # of successes in # of trials. 

```{r}
bin_probability(2, 5,  0.5)
bin_probability(0:2,  5, 0.5)
bin_probability(55, 100, 0.45)
```

## Function bin_distribution()

This function returns a data frame with the probability distribution: sucesses in
the first column, probability in the second column.

It also graphs a barplot to display the probability histogram of a binomial distribution object "bindis".

```{r}
x <- bin_distribution( 5, 0.5)
x
plot(x)
```

## Function bin_cumulative()

This function returns a data frame with both the probability distribution and the
cumulative probabilities: sucesses in the first column, probability in the second column,
and cumulative in the third column.

It also graphs the cumulative distribution in ab object "bincum".
```{r}
y <- bin_cumulative( 5,  0.5)
y
plot(y)
```

## Function bin_variable()

This function returns an object of class "binvar", that is, a binomial random
variable object.

Summary function returns a list of class "summary.binvar" containing named elements

```{r}
bin1 <- bin_variable(10, 0.3)
bin1
summary(bin1)
```

## Function bin_mean()

This function returns a mean 

```{r}
bin_mean(10, 0.3)
```

## Function bin_variance()

This function returns a variance 

```{r}
bin_variance(10, 0.3)
```

## Function bin_mode()

This funciton returns a mode

```{r}
bin_mode(10, 0.3)
```

## Function bin_skewness()

This function returns a skewness

```{r}
bin_skewness(10, 0.3)
```

## Function bin_kurtosis()

This function returns a kurtosis

```{r}
bin_kurtosis(10, 0.3)
```

